---
title: Analysis codes for the paper "Pygoscelis penguin breeding success along the
  Western Antarctic Peninsula under contrasting krill biomass and fixed catch limit"
author: "Lucas Krüger, Francisco Santa Cruz, Mauricio Mardones, César Cárdenas"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document:
    fig_width: 10
    fig_height: 8
  pdf_document: default
---
#Load necessary packages

```{r, echo=TRUE}
library(plyr)
library(dplyr) # for summarizing data
library(reshape2)
library(ggplot2)  # plotting 
library(sjPlot)
library(patchwork)
library(lubridate) # to deal with time data
library(udunits2) # to deal with geographical data
library(raster)
library(MCMCglmm) #Bayesian generalized linear mixed models
library(lmerTest)
library(rcompanion)
library(lmPerm)
library(ggsignif)
library(energy)


```

###--------penguins-------------

#load data

### data from MAPPPD (penguinmap.org): Humphries et al. 2017 https://doi.org/10.1017/S0032247417000055

```{r,echo=TRUE}
peng<-readRDS("D:/BACKUP_Notebook_06_2022/KidsArentAlright/Project/MAPPPD.Rds") # query for area 48.1 

nests<-subset(peng,count_type=="nests",
              select=c(site_name,site_id,longitude_epsg_4326,latitude_epsg_4326,
                       common_name,day,month,season_starting,penguin_count,
                       count_type,vantage,accuracy))


chicks<-subset(peng,count_type=="chicks",
               select=c(site_name,site_id,longitude_epsg_4326,latitude_epsg_4326,
                        common_name,day,month,season_starting,penguin_count,
                        count_type,vantage,accuracy))
nestsM<-ddply(nests, c("common_name","site_name","site_id","season_starting"), summarise,
              nests=max(penguin_count),
              Lat=mean(latitude_epsg_4326),
              Long=mean(longitude_epsg_4326))
chicksM<-ddply(chicks, c("common_name","site_name","site_id","season_starting"), summarise,
               chicks=min(penguin_count),
               Lat=mean(latitude_epsg_4326),
               Long=mean(longitude_epsg_4326))

cpn<-merge(nestsM,chicksM)
cpn$chickspernest<-cpn$chicks/cpn$nests  ### measure of breeding success (chicks raised per nest)

cpn2<-data.frame(site=cpn$site_id,SP=cpn$common_name,
                 Year=cpn$season_starting,
                 Long=as.numeric(cpn$Long),
                 Lat=as.numeric(cpn$Lat),
                 chickspernest=cpn$chickspernest) # cpn stands for Chicks Per Nest

#### this is for summarizing number of populations and number of counts

cpnset<-cpn2 

counts<-ddply(cpnset, c("SP"), summarise,
              ncounts=length(chickspernest))

counts

pops<-ddply(cpn2, c("SP","site"), summarise,
            pops=length(chickspernest),
            Lat=mean(Lat),Long=mean(Long))


pops2<-ddply(pops, c("SP"), summarise,
             Npops=length(pops))

sites<-ddply(cpn, c("site_id"), summarise,
             Ncounts=length(chicks))

cpn$chickspernest<-cpn$chicks/cpn$nests  ### measure of breeding success (chicks raised per nest)

cpn<-merge(cpn,sites,by="site_id")

summary(cpn$nests)

ggplot(cpn,aes(nests))+geom_histogram()+xlim(0,10000)
ggplot(cpn,aes(nests))+geom_histogram()+xlim(0,100) # check small populations
ggplot(cpn,aes(nests,chickspernest))+geom_point() # a single large population will be excluded too


### eliminate pops with success = 2, as they were two cases of one or two nests
### eliminate the single population with 80 000 nests

cpn<-subset(cpn,chickspernest<2 & nests<40000) # assuming any estimation of success above 2 would mean imprecise counts

summary(cpn$chickspernest)

cpn<-subset(cpn,Ncounts>3) # only colonies with more than 3 counts

shapiro.test(cpn$chickspernest) # not normal 

ggplot(cpn,aes(season_starting,chickspernest))+geom_point()+
  geom_vline(xintercept = 1990)+
  geom_smooth(method="lm",se=F)+facet_wrap(site_id~.)+theme_bw()

#the plot above shows us that there was site-level slope variability and there was few sites with data previous to 1990. So, further filters:

cpn<-subset(cpn,season_starting>1989)

cpn<-subset(cpn,site_id!="SELV" & site_id!="SPTR") 

shapiro.test(cpn$chickspernest) # not normal 
shapiro.test(cpn$chickspernest[cpn$chickspernest>0.5]) # normal if eliminate values lower than 0.5
cpn<-subset(cpn, chickspernest>0.5)
ggplot(cpn,aes(chickspernest))+geom_histogram()+theme_bw()+xlab("Chicks raised per nest")

### test if chicks per nest varied in time using sites  as random factors

cpn$Zss<-scale(cpn$season_starting,center=T) # scaling the time variable


cpn$site_id2<-factor(cpn$site_id,levels=c("LLAN","ARDL","BART","SHIR","HALF","ENTR",
                                          "BROW","SPIP","ORNE","GEOR","LITC","DOBE","DAMO","LOCK",
                                          "JOUG","NEKO","ALMI","PCHA","PLEN","PETE"))  # order by location latitude

cpn$site_name2<-factor(cpn$site_name,levels=c("Llano Point","Ardley Island","Barton Peninsula",
                                              "Cape Shirreff","Half Moon Island","Entrance Point",
                                              "Brown Bluff","Spigot Peak Point","Orne Islands",
                                              "Georges Point (Ronge Island)","Litchfield Island",
                                              "Dorian Beacon","Dorian Bay/Damoy Point","Port Lockroy",
                                              "Jougla Point","Neko Harbor (Andvord Bay)",
                                              "Brown Station","Port Charcot",
                                              "Pleneau Island","Petermann Island"))  # order by location latitude

#species summaries 

length(unique(cpn$site_id[cpn$common_name=="adelie penguin"]))
length((cpn$site_id[cpn$common_name=="adelie penguin"]))

length(unique(cpn$site_id[cpn$common_name=="chinstrap penguin"]))
length((cpn$site_id[cpn$common_name=="chinstrap penguin"]))


length(unique(cpn$site_id[cpn$common_name=="gentoo penguin"]))
length((cpn$site_id[cpn$common_name=="gentoo penguin"]))


(ggplot(cpn,aes(season_starting,chickspernest))+geom_point(size=1,alpha=0.5)+
    geom_smooth(method="lm",se=F)+facet_wrap(site_name2~.)+theme_bw()+theme(panel.spacing.x = unit(1.5, "lines")))

lmer1<-lmer(chickspernest~Zss+(Zss|site_id),data=cpn)  #previous picture justified the structure of the random term (there was site-level slope variability)

isSingular(lmer1)# convergence problems detected

#therefore, a Bayesian evaluation with flexible priors is justified to avoid convergence issues 

prior<- list(R = list(V = 1, nu = 0.002),
             G = list(G1 = list(V = diag(2), nu = 0.002,
                                alpha.mu = rep(0, 2),
                                alpha.V= diag(2, 2, 2))))

mc1<-MCMCglmm(chickspernest~season_starting, random=~us(1 + Zss):site_id, rcov=~units, 
              
              family="gaussian",
              data=cpn, nodes="ALL",  scale=TRUE, nitt=10999, thin=1, burnin=1000, pr=T,
              pl=FALSE, verbose=TRUE, DIC=TRUE, singular.ok=FALSE, saveX=TRUE,
              saveZ=TRUE, saveXL=TRUE, slice=FALSE, ginverse=NULL, trunc=FALSE,
              prior= prior)


summary(mc1) # no significance
#adjust plot margins
par(mar = c(1, 1, 1, 1))

#create plot
plot(5:20)

plot(mc1$Sol) # diagnostic plots for site effects majority of posteriors distributions were acceptable
plot(mc1$VCV) # diagnostic plots for random effects were acceptable

#proportion of the effective sample size: we want a low number as it indicates model converged with less iterations
summary(mc1)$solutions[2,4]/10999 

sol<-data.frame(mc1$Sol) # random effects

solm<-melt(sol,id.vars=c("X.Intercept.","season_starting"))

solm$vars<-substring(solm$variable,first=1,last=4)

slm<-subset(solm,vars=="Zss.") #select slopes

tail(slm)

slm$site_id<-substring(slm$variable,first=13,last=17)


sites<-ddply(cpn, c("site_id"), summarise,
             pops=length(chickspernest),
             Lat=mean(Lat),Long=mean(Long))

ranef<-ddply(slm, c("site_id"), summarise,
             slp=mean(season_starting),slpsd=sd(season_starting),
             slpse=slpsd/sqrt(length(value)-1),
             med=median(value),
             q95=quantile(value,prob=0.95),
             q05=quantile(value,prob=0.05))

rlat<-merge(slm,sites,by="site_id")

ranef<-ddply(slm, c("site_id"), summarise,
             slp=mean(value),slpsd=sd(value),
             slpse=slpsd/sqrt(length(value)-1),
             med=median(value),
             q95=quantile(value,prob=0.95),
             q05=quantile(value,prob=0.05))

rlat<-merge(ranef,sites,by="site_id")

rlat$Lat_ID<-paste(rlat$Lat,rlat$site_id)

rlat$local<-ifelse(rlat$Lat<(-63.2),"Peninsula","South Shetlands")

pairwisePermutationTest(slp~local,data=rlat) # difference is marginally significant

(ggplot(rlat,aes(local,slp))+geom_boxplot()+
    theme_bw()+xlab("")+ylab("Random slope")+coord_flip()+
    geom_signif(
      comparisons = list(c("Peninsula","South Shetlands")),
      map_signif_level = F,step_increase = 0.075,
      test="wilcox.test", # could not change the Wilcox test for the permutation results, but this is just for plotting
      textsize = 3))


```

#load krill acoustic data from "WG-ASAM Results from the WG-ASAM Intersessional e-Group on Krill Biomass Estimates from Acoustic Surveys; 2021;"

```{r,echo=TRUE}


krill<-readRDS("D:/BACKUP_Notebook_06_2022/KidsArentAlright/Project/CCAMLR_krill_biomass.Rds") # data from WG-ASAM e-group (2021)


krill2<-subset(krill,
               Strata=="Bransfield"|Strata=="West") ### subset the strata 
                                                    ### where fishing has been consistent

```


#load and process fishing data 

```{r,echo=TRUE}
kf0<-read.csv("D:/BACKUP_Notebook_06_2022/KidsArentAlright/Data/C1_Sect.csv") ### fishing data from CCAMLR, this is the raw data, not available freely (only the CCAMLR secretariat is allowed to distribute it) 

kf0$CatchT<-kf0$KrillCaughtKG/1000  ### catch in tones

kf0$ts<- as.POSIXct(strptime(kf0$Day,format="%m/%d/%Y" ,tz="GMT")) 

kf0$month<-month(kf0$ts)

kf0$FSeason<-ifelse(kf0$month>11,
            kf0$CalendarYear,kf0$CalendarYear-1) ### fishing season starts in december
                                                 ### january up to november next year
                                                 ### is assigned to the season of the previous year
                                                 ### krill season however, places december to the
                                                 ### following year, 
                                                 ### therefore fishing season 2018=krill season 2019
                                                 
kf<-kf0

strata<-shapefile("D:/BACKUP_Notebook_06_2022/KidsArentAlright/Data/Shapefiles/AMLR_STRATA_.shp")  ### from CCAMLR as well (AMLR_strata.Rds)

crs=CRS( "+proj=longlat +datum=WGS84 +no_defs")

kcoords<-coordinates(data.frame(x=kf$FishingLon,y=kf$FishingLat))

kf.spdf<-SpatialPointsDataFrame(kcoords,kf,proj4string = crs)

kf.strata<-over(kf.spdf,strata)

kf.spdf$Strata<-kf.strata$Strata


kf.spdf<-subset(kf.spdf,FishingLon<(-50))  # eliminate the South Orkney Data 

```

#### bring krill and fishery together

```{r,echo=TRUE}

kf.spdf$Year<-kf.spdf$CalendarYear

### months with krill estimation

kfMo<-subset(kf.spdf,month=="12"|month=="1"|month=="2"|month=="3") 

fcr2<-ddply((data.frame(kfMo)), c("Year","Strata"), summarise,
            CatchS=sum(CatchT))  ### total catch for each year and strata

# this is the data we made available (CCAMLR_krill_fishing_catch.Rds), already summarized fishing data; 

summary(fcr2) ### CatchS is catch in Ton

head(krill) ### amlrbiomass is in ton

kr<-data.frame(krill[1],krill[2],krill[14]) # keep only needed variables

kmfcr<-merge(kr,fcr2,by=c("Strata","Year"),all=T)  # merge krill and fishery data 

kmfcr2<-subset(kmfcr,Year<2019 & Year>1994) 

# check 1st quantiles to fill missing values
summary(kmfcr2$amlrbiomass[kmfcr2$Strata=="Bransfield"]) 
summary(kmfcr2$amlrbiomass[kmfcr2$Strata=="West"])

kmfcr2$amlrbiomass[is.na(kmfcr2$amlrbiomass) & kmfcr2$Strata=="Bransfield"]<-392888# 1st qu
kmfcr2$amlrbiomass[is.na(kmfcr2$amlrbiomass) & kmfcr2$Strata=="West"]<-752566# 1st qu

# substitute missing values by 0 (no catch)
summary(kmfcr2$CatchS[kmfcr2$Strata=="West"])
summary(kmfcr2$CatchS[kmfcr2$Strata=="Bransfield"])

kmfcr2$CatchS[is.na(kmfcr2$CatchS) & kmfcr2$Strata=="West"]<-0 # 1st qu
kmfcr2$CatchS[is.na(kmfcr2$CatchS) &  kmfcr2$Strata=="Bransfield"]<-0 # 1st qu

kmfcr2$Strata<-factor(kmfcr2$Strata,levels=c("West","Bransfield"))

summary(kmfcr2$amlrbiomass/1000)
kmfcr2$CatchK<-kmfcr2$CatchS/kmfcr2$amlrbiomass # harvest rate 


kmfcr2$State[(kmfcr2$amlrbiomass/1000)<1251.728 & kmfcr2$Strata=="West"]<-"Biomass < mean"
kmfcr2$State[(kmfcr2$amlrbiomass/1000)<802.284 & kmfcr2$Strata=="Bransfield"]<-"Biomass < mean"
kmfcr2$State[(kmfcr2$amlrbiomass/1000)<200]<-"Near or below catch limit"
kmfcr2$State[is.na(kmfcr2$State)]<-"Biomass > mean"

plot2a<-ggplot()+
  geom_hline(yintercept=155,linetype="dotted",colour="red")+
  geom_hline(yintercept=1251.728,linetype="dashed")+
  geom_hline(yintercept=802.284,linetype="dashed")+
  geom_smooth(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
              aes(x=Year,y=(amlrbiomass/1000)),
    
    
    method="lm",se=F,fullrange=F,formula=y~x)+xlim(1995,2018)+
  geom_point(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
             aes(x=Year,y=(amlrbiomass/1000),colour=State),size=2)+theme_bw()+facet_wrap(~Strata)+
  ggtitle(label="a. krill biomass")+
  scale_colour_manual(values=c("yellow3","green2","red2"))+
  ylab("thousand tonnes")+xlab("") # figure X


plot2b<-ggplot()+
  geom_hline(yintercept=5,linetype="dotted",colour="red")+geom_point()+
  
  geom_smooth(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
              aes(x=Year,y=(CatchK*100)),method="lm",se=F,fullrange=F,span=0.9)+xlim(1995,2018)+
  geom_point(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
             aes(x=Year,y=(CatchK*100),colour=State),size=2)+theme_bw()+facet_wrap(~Strata)+
  ggtitle(label="b. krill caught biomass")+
  scale_colour_manual(values=c("yellow3","green2","red2"))+
  ylab("% of catched biomass") # figure X


plot2c<-ggplot()+
  geom_hline(yintercept=5,linetype="dashed")+geom_point()+
  geom_vline(xintercept=1251.728,linetype="dashed")+
  geom_vline(xintercept=802.284,linetype="dashed")+
  geom_smooth(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
              aes(x=(amlrbiomass/1000),y=(CatchK*100)),
              method="gam",se=F,fullrange=F,span=0.9)+
  geom_point(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
             aes(x=(amlrbiomass/1000),y=(CatchK*100),colour=State),size=2)+theme_bw()+facet_wrap(~Strata)+
  ggtitle(label="c. availability vs catch")+
  scale_colour_manual(values=c("yellow3","green2","red2"))+
  ylab("% of catched biomass")+ 
  xlab("Krill biomass (million tonnes)") # figure X

plot2a/plot2b/plot2c # figure 2



```

### Testing whether krill biomass changed in time 

```{r,echo=TRUE}

kmfcr2<-na.omit(kmfcr2)

ggplot(kmfcr2,aes(amlrbiomass))+geom_histogram()+theme_bw()

poisson.mtest(as.integer(kmfcr2$amlrbiomass),R=99)  ##test for poisson distribution. Yes it is


glm1<-glm(amlrbiomass~Year,data=subset(kmfcr2,Strata=="West"),family="poisson")
glm2<-glm(amlrbiomass~Year,data=subset(kmfcr2,Strata=="Bransfield"),family="poisson")

summary(glm1) 
summary(glm2)


#diagnsotics:

library(AER)
dispersiontest(glm1)

res <- residuals(glm1, type="deviance")
plot(log(predict(glm1)), res) # seems ok
abline(h=0, lty=2)
qqnorm(res)
qqline(res)


dispersiontest(glm2)

res2 <- residuals(glm2, type="deviance")
plot(log(predict(glm2)), res2) # seems ok
abline(h=0, lty=2)
qqnorm(res2)
qqline(res2)

```

### Penguins and fishery
### transfer strata information into penguin data

```{r,echo=TRUE}
pcoords<-coordinates(data.frame(cpnset[4:5])) 

p.spdf<-SpatialPointsDataFrame(pcoords,cpnset,proj4string = crs)

identicalCRS(p.spdf,strata)

p.strata<-over(p.spdf,strata)

p.spdf$Strata<-p.strata$Strata

p.spdf$StrataP<-p.spdf$Strata


####merge penguins and fishery

p.df<-data.frame(p.spdf)

peng<-data.frame(p.df[1:8]) ## maintain in the data only variables to analyze

summary(as.factor(peng$StrataP))


peng.f<-merge(peng,kmfcr2,all.x=T)  ## merge and maintain all penguin data

pengf<-subset(peng.f,StrataP==Strata)#if penguin and fishing strata coincides, then it is right

pengf$harvest<-pengf$CatchS/pengf$amlrbiomass # catch per unit of krill biomass (harvest rate)

ggplot(pengf,aes(harvest,chickspernest))+ #figure supp2
  
  geom_point()+
  theme_bw()+
  xlab("% of caught biomass (harvest rate)")+ylab("chicks raised per nest")+
  geom_vline(xintercept=0.05,linetype="dashed") #5% catch

pengf$HR<-ifelse(pengf$harvest>0.05,">5%","<5%")

pengf<-na.omit(pengf)

pengf$KrillC<-pengf$State

summary(as.factor(pengf$KrillC))

pengf$KrillC[pengf$KrillC=="Near or below catch limit"]<-"Biomass < mean"


ddply(pengf, c("HR","KrillC"), summarise,
      ncounts=length(chickspernest))

shapiro.test(pengf$chickspernest)#not normal


shapiro.test(pengf$chickspernest[pengf$chickspernest>0.5]) # normal if eliminating values below 0.5

pengf2<-subset(pengf,chickspernest>0.5)

ggplot(pengf,aes(chickspernest))+geom_histogram()+theme_bw()+
  ggplot(pengf2,aes(chickspernest))+geom_histogram()+theme_bw() # visualize two distributions

summary(as.factor(pengf2$HR))
summary(as.factor(pengf2$KrillC))
unique(pengf2$site)


pengf2$HRK<-paste(pengf2$KrillC,pengf2$HR,sep=", Catch") # harvest rate and krill categories
summary(as.factor(pengf2$HRK)) 

pengf2$HRK2<-factor(pengf2$HRK,levels=c("Biomass > mean, Catch<5%",
                                        "Biomass < mean, Catch<5%",
                                        "Biomass < mean, Catch>5%"))

bartlett.test(pengf2$chickspernest,pengf2$HRK2) # homogeneity is marginal


summary(as.factor(pengf2$HRK2))


lmer2<-lmer(chickspernest~HRK2+(harvest|site),data=pengf2)

anova(lmer2,ddf="Satterthwaite",type = "III")
lsmeansLT(lmer2)

ranova(lmer2)

plot_model(lmer2,type="diag")

plot_model(lmer2,type="re",grid=F)

(ggplot(pengf2,aes(HRK2,chickspernest))+
    geom_hline(yintercept=1,linetype="dashed",linewidth=1)+
    geom_boxplot()+
    theme_bw()+xlab("")+ylab("Chicks raised per nest")+coord_flip()+
    geom_signif(
      comparisons = list(c("Biomass > mean, Catch<5%","Biomass < mean, Catch<5%"),
                         c("Biomass < mean, Catch<5%","Biomass < mean, Catch>5%"),
                         c("Biomass > mean, Catch<5%","Biomass < mean, Catch>5%")),
      map_signif_level = F,step_increase = 0.075,
      test="t.test", # could not change it to the permutation results, but this is just for plotting
      textsize = 3))
max(pengf3$CatchS)

# next plots are just to explore a little bit more...
pengf3<-subset(pengf2,site!="AITC" & site!="HANN"& site!="PTHO")

ggplot()+geom_point(data=pengf3,aes(x=CatchS,y=chickspernest,colour=KrillC,shape=SP))+
  theme_bw()+theme(panel.spacing.x = unit(1.5, "lines"),
                   axis.text.x = element_text(angle=90))+
  geom_smooth(method="lm",se=F,
              data=pengf3,aes(x=CatchS,y=chickspernest,colour=KrillC))+
  scale_colour_manual(values=c("red","blue"),name="Krill availability")+
  facet_wrap(site~.)+xlim(0,50000)+
  xlab("Accumulated summer fishing catch (t)")+ ylab("Penguin chicks raised per nest")


#taking only sites with multiple samples in contrasting krill availabilkity: at ARDL, BART (neighbor areas) increased catch in years with low krill biomass meant decreasing breeding success;  Shireff is the only site in the Drake passage, and trends were inverted; but there was no samples in years with very hich catch...


### that's all folks!

```
