---
title: Routine, analysis and suplementary material for the ms "Pygoscelis penguin
  breeding success along the Western Antarctic Peninsula under contrasting krill biomass
  and fixed catch limits"
author: "Lucas Krüger, Maurício Mardones, Francisco Santa Cruz, César Cárdenas"
date: '`r Sys.Date()`'
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# BACKGROUND

This document contains the codes for: 

- 1. evaluate temporal trends of Pygoscelis penguin breeding success in the South Shetland Islands and Antarctic Peninsula; 

- 2.  evaluate temporal variability of krill biomass in relation to fishing harvest; 

- 3. compare penguin breeding success in periods of low or high krill biomass and low or high fishing catches. 


```{r library}
### Load necessary packages
library(plyr)
library(dplyr) 
library(reshape2)
library(ggplot2)  
library(sjPlot)
library(patchwork)
library(raster)
library(lmerTest)
library(rcompanion)
library(lmPerm)
library(ggsignif)
library(ggthemes)
library(ggpubr)
library(fitdistrplus)
library(AER)
library(easystats)
library(formatR)
library(lubridate)
```

# DATA

Four data sources were used: 



- CCAMLR acoustic estimates of krill biomass `CCAMLR_krill_biomass.Rds`, 

- Summarized fishing catch `CCAMLR_krill_fishing_catch.Rds`

- Management strata shapefiles `AMLR_Strata.Rds`. 

- [MAPPPD data](Humphries et al. 2017 https://doi.org/10.1017/S0032247417000055) [@Humphries2017], file named `MAPPPD.Rds` 

Refer to the manuscript for methodological details.


# ANALISYS ROUTINE

### krill and fishery data 

krill acoustic biomass from "WG-ASAM Results from the WG-ASAM Intersessional e-Group on Krill Biomass Estimates from Acoustic Surveys; 2021;" data from WG-ASAM e-group (2021) and subset the strata where fishing has been consistent

Fishing data from CCAMLR, this is the raw data, not available freely (only the CCAMLR secretariat is allowed to distribute it) 


```{r}
### Load krill acoustic dataand subset to the target strata


krill<-readRDS("CCAMLR_krill_biomass.Rds")  


### Load and prepare fishery data 

kf0<-read.csv("C1_Sect.csv") # ps: this data is not available here, only the already summarized data resulting from next steps

kf0$CatchT<-kf0$KrillCaughtKG/1000  ### catch in tones

kf0$ts<- as.POSIXct(strptime(kf0$Day,format="%m/%d/%Y" ,tz="GMT")) 

kf0$month<-month(kf0$ts)

kf0$FSeason<-ifelse(kf0$month>11,
                    kf0$CalendarYear,kf0$CalendarYear-1) # fishing season starts in december each year
                                                         # for instance,the fishing season 2012 is from december 2012 to novmeber 2013
kf0$Kseason<-kf0$FSeason+1                               
kf<-kf0


strata<-readRDS("AMLR_STRATA.Rds")                       # strata for fishing management

crs=CRS( "+proj=longlat +datum=WGS84 +no_defs")

kcoords<-coordinates(data.frame(x=kf$FishingLon,
                                y=kf$FishingLat))

kf.spdf<-SpatialPointsDataFrame(kcoords,kf,
                                proj4string = crs)

kf.strata<-over(kf.spdf,strata)                          # place fishing into strata
kf.spdf$Strata<-kf.strata$Strata
kf.spdf<-subset(kf.spdf,FishingLon<(-50))                # eliminate the South Orkney Data 

kf.spdf$Year<-kf.spdf$Kseason



kfMo<-subset(kf.spdf,
      month=="12"|month=="1"|month=="2"|month=="3")     # select fishery data in the periods where acoustic biomass was estimated


fcr2<-ddply((data.frame(kfMo)), c("Year","Strata"), summarise,
            CatchS=sum(CatchT))                        # total catch for each year and strata

summary(fcr2) ### CatchS is catch in Ton

kr<-data.frame(krill[1],krill[2],krill[14]) # keep only needed variables from krill acoustic data

kmfcr<-merge(kr,fcr2,by=c("Strata","Year"),all=T)  # merge krill and fishery data 

kmfcr2<-subset(kmfcr,Year<2019 & Year>1994)

### summarize data per strata and substitute krill acoustic missing values by the 1st quantile
### this follows the rationale that the 1st quantil for estimating allowed catch is precautionary

summary(kmfcr2$amlrbiomass[kmfcr2$Strata=="Bransfield" | kmfcr2$Strata=="West"]) 

summary(kmfcr2$amlrbiomass[kmfcr2$Strata=="Bransfield"]) 
summary(kmfcr2$amlrbiomass[kmfcr2$Strata=="West"])
kmfcr2$amlrbiomass[is.na(kmfcr2$amlrbiomass) & kmfcr2$Strata=="Bransfield"]<-392888# 1st qu
kmfcr2$amlrbiomass[is.na(kmfcr2$amlrbiomass) & kmfcr2$Strata=="West"]<-752566# 1st qu

### no catch data means no fishing occurred. So, missing catch data was replaced by 0

summary(kmfcr2$CatchS[kmfcr2$Strata=="West"])
summary(kmfcr2$CatchS[kmfcr2$Strata=="Bransfield"])
kmfcr2$CatchS[is.na(kmfcr2$CatchS) & kmfcr2$Strata=="West"]<-0 
kmfcr2$CatchS[is.na(kmfcr2$CatchS) &  kmfcr2$Strata=="Bransfield"]<-0 
kmfcr2$Strata<-factor(kmfcr2$Strata,levels=c("West","Bransfield"))


kmfcr2$CatchK<-kmfcr2$CatchS/kmfcr2$amlrbiomass # harvest rate 
kmfcr2$State[(kmfcr2$amlrbiomass/1000)<1251.728 & kmfcr2$Strata=="West"]<-"Biomass < mean"
kmfcr2$State[(kmfcr2$amlrbiomass/1000)<802.284 & kmfcr2$Strata=="Bransfield"]<-"Biomass < mean"
kmfcr2$State[(kmfcr2$amlrbiomass/1000)<200]<-"Near or below catch limit"
kmfcr2$State[is.na(kmfcr2$State)]<-"Biomass > mean"

kmfcr2$State<-factor(kmfcr2$State,levels=c("Biomass > mean","Biomass < mean","Near or below catch limit"))



fig3a<-ggplot()+
  geom_hline(yintercept=155,linetype="dotted",colour="red")+
  geom_hline(yintercept=1251.728,linetype="dashed")+
  geom_hline(yintercept=802.284,linetype="dashed")+
  geom_smooth(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
              aes(x=Year,y=(amlrbiomass/1000)),
              method="lm",se=F,
              fullrange=F,
              formula=y~x)+
  xlim(1995,2018)+
  geom_point(data=subset(kmfcr2,
                         Strata=="Bransfield"|Strata=="West"),
             aes(x=Year,y=(amlrbiomass/1000),
                 colour=State),size=2)+
  theme_bw()+
  facet_wrap(~Strata)+
  ggtitle(label="a. krill biomass")+
  scale_colour_manual(values=c("green2","yellow3","red2"))+
  ylab("thousand tonnes")+xlab("") # figure X


fig3b<-ggplot()+
  geom_hline(yintercept=5,linetype="dotted",colour="red")+geom_point()+
  
  geom_smooth(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
              aes(x=Year,y=(CatchK*100)),method="lm",se=F,fullrange=F,span=0.9)+xlim(1995,2018)+
  geom_point(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
             aes(x=Year,y=(CatchK*100),colour=State),size=2)+theme_bw()+facet_wrap(~Strata)+
  ggtitle(label="b. krill caught biomass")+
  scale_colour_manual(values=c("green2","yellow3","red2"))+
  ylab("% of catched biomass") # figure X


fig3c<-ggplot()+
  geom_hline(yintercept=5,linetype="dashed")+geom_point()+
  geom_vline(xintercept=1251.728,linetype="dashed")+
  geom_vline(xintercept=802.284,linetype="dashed")+
  geom_smooth(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
              aes(x=(amlrbiomass/1000),
                  y=(CatchK*100)),
              method="gam",se=F,
              fullrange=F,span=0.9)+
  geom_point(data=subset(kmfcr2,
                         Strata=="Bransfield"|Strata=="West"),
             aes(x=(amlrbiomass/1000),
                 y=(CatchK*100),
                 colour=State),size=2)+
  theme_bw()+facet_wrap(~Strata)+
  ggtitle(label="c. availability vs catch")+
  scale_colour_manual(values=c("green2","yellow3","red2"))+
  ylab("% of catched biomass")+ 
  xlab("Krill biomass (million tonnes)") # figure X

fig3a/fig3b/fig3c # fig 2

kmfcr3<-na.omit(kmfcr2)

```

#is krill biomass reducing? Test if biomass in periods of high krill productivity is decreasing

```{r}
### removing outliers 
quartiles <- quantile(log(kmfcr3$amlrbiomass), probs=c(.2, .8), na.rm = FALSE)
IQR <- IQR(log(kmfcr3$amlrbiomass))

Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 

data_no_outlier <- subset(kmfcr3, log(amlrbiomass) > Lower & log(amlrbiomass) < Upper)

data_no_outlier$State[data_no_outlier$State=="Near or below catch limit"]<-"Biomass < mean"

shapiro.test(log(data_no_outlier$amlrbiomass)[data_no_outlier$State=="Biomass > mean"]) # normal
bartlett.test(log(data_no_outlier$amlrbiomass)[data_no_outlier$State=="Biomass > mean"],data_no_outlier$Strata[data_no_outlier$State=="Biomass > mean"]) # homogeneous variance


plotdist(log(data_no_outlier$amlrbiomass[data_no_outlier$State=="Biomass > mean"]),"norm",
         para=list(mean=mean(log(data_no_outlier$amlrbiomass[data_no_outlier$State=="Biomass > mean"])), 
                   sd=sd(log(data_no_outlier$amlrbiomass[data_no_outlier$State=="Biomass > mean"]))))

glm1<-lm(log(amlrbiomass)~Year+Strata,
         data=subset(data_no_outlier,State=="Biomass > mean"))


posterior_predictive_check(glm1,iterations=300)
plot(check_outliers(glm1))
plot(check_collinearity(glm1))

anova(glm1) # krill biomass reduced significantly in time

summary(glm1) # reduction was steeper in West Strata in relation to Bransfield



```


### Penguins and fishery

### load penguin data and merge with previous datasets to answer the questions: does increased catches can affect penguin breeding success in a decreasing krill biomass context?

```{r}

peng<-readRDS("MAPPPD.Rds") 

nests<-subset(peng,
              count_type=="nests",
              select=c(site_name,
                       site_id,
                       longitude_epsg_4326,
                       latitude_epsg_4326,
                       common_name,
                       day,
                       month,
                       season_starting,
                       penguin_count,
                       count_type,
                       vantage,accuracy))

chicks<-subset(peng,count_type=="chicks",
               select=c(site_name,
                        site_id,longitude_epsg_4326,
                        latitude_epsg_4326,
                        common_name,
                        day,month,season_starting,penguin_count,
                        count_type,vantage,accuracy))

nestsM<-ddply(nests, c("common_name",
                       "site_name",
                       "site_id",
                       "season_starting"), 
              summarise,
              nests=max(penguin_count),
              Lat=mean(latitude_epsg_4326),
              Long=mean(longitude_epsg_4326))

chicksM<-ddply(chicks, c("common_name",
                         "site_name",
                         "site_id",
                         "season_starting"),
               summarise,
               chicks=min(penguin_count),
               Lat=mean(latitude_epsg_4326),
               Long=mean(longitude_epsg_4326))

cpn<-merge(nestsM,chicksM) # cpn stands for Chicks Per Nest


cpn$chickspernest<-cpn$chicks/cpn$nests # breeding success measured as chicks raised per nest


sites<-ddply(cpn, c("site_id"), summarise,
             Ncounts=length(chicks))


pcoords<-coordinates(data.frame(cpn[6:5])) 

plot(pcoords)

p.spdf<-SpatialPointsDataFrame(pcoords,cpn,proj4string = crs)

identicalCRS(p.spdf,strata)

p.strata<-over(p.spdf,strata) # place each colony at one stratum

p.spdf$Strata<-p.strata$Strata
p.spdf$StrataP<-p.spdf$Strata

p.df<-data.frame(p.spdf)
peng<-data.frame(p.df) 

peng$Year<-peng$season_starting

cpn<-merge(cpn,sites,by="site_id") 

peng.f<-merge(peng,kmfcr2,by=c("Strata","Year"))  ## merge penguin data with krill and fishery data

summary(as.factor(peng.f$site_id))

pengf<-na.omit(subset(peng.f,StrataP==Strata)) #if penguin and fishing strata coincides, then it is right

summary(as.factor(pengf$site_id))

pengf$harvest<-pengf$CatchS/pengf$amlrbiomass # catch per unit of krill biomass (harvest rate)


### classify harvest rate and krill availability 

# supplemental figure 4

ggplot(pengf,aes(harvest*100,chickspernest))+
  geom_vline(xintercept = 5,linetype="dotted")+
  geom_smooth(method="lm")+
  geom_point()+
  xlab("Harvest rate (%)")+ylab("Penguin chicks raised per nest")+
  theme_bw()



pengf$HR<-ifelse(pengf$harvest>0.05,">5%","<5%")
pengf<-na.omit(pengf)
pengf$KrillC<-pengf$State
summary(as.factor(pengf$KrillC))

pengf$KrillC[pengf$KrillC=="Near or below catch limit"]<-"Biomass < mean"

ddply(pengf, c("HR","KrillC"), summarise,
      ncounts=length(chickspernest))


unique(pengf$site_id)
summary(as.factor(pengf$site_id))

pengf$HRK<-paste(pengf$KrillC,pengf$HR,sep=", Catch") # harvest rate and krill categories
summary(as.factor(pengf$HRK)) 
pengf$HRK2<-factor(pengf$HRK,levels=c("Biomass > mean, Catch<5%",
                                      "Biomass < mean, Catch<5%",
                                      "Biomass < mean, Catch>5%"))

bartlett.test(pengf$chickspernest,pengf$HRK2) # homogeneity of variances

summary(as.factor(pengf$HRK2))





```

### statistical analysis 

### first: for these colonies, is there any consistent temporal trend?

```{r}


lmadp<-lm(season_starting~chickspernest,data=subset(pengf,common_name=="adelie penguin"))
summary(lmadp) # no 

lmchp<-lm(season_starting~chickspernest,data=subset(pengf,common_name=="chinstrap penguin"))
summary(lmchp) # no 

lmgep<-lm(season_starting~chickspernest,data=subset(pengf,common_name=="gentoo penguin"))
summary(lmgep)# no

posterior_predictive_check(lmadp,iterations=300)
posterior_predictive_check(lmchp,iterations=300)
posterior_predictive_check(lmgep,iterations=300)

check_heteroscedasticity(lmadp)
check_heteroscedasticity(lmchp)
check_heteroscedasticity(lmchp)



```

# second does breeding success varies accordingly to krill availability and harvest rate?

```{r}

lmer2<-lmer(chickspernest~HRK2+(1|site_id),
            data=pengf)
anova(lmer2,
      ddf="Satterthwaite",
      type = "III")


summary(lmer2)

ranova(lmer2)

plot_model(lmer2,type="re") 

posterior_predictive_check(lmer2,iterations=300)
check_outliers(lmer2) # one outlier 

check_homogeneity(lmer2)

check_heteroscedasticity(lmer2)

# eliminate the outlier and try again 

pf<-subset(pengf,chickspernest>0.1)

lmer2b<-lmer(chickspernest~HRK2+(1|site_id),
            data=pf)
anova(lmer2b) # marginally significant

summary(lmer2b) # breeding success during periods of low biomass and high catch was different from periods of high biomass and low catch

ranova(lmer2b)  # consistent between places


posterior_predictive_check(lmer2b,iterations=900) # acceptable
check_outliers(lmer2b) 

check_homogeneity(lmer2b)

check_heteroscedasticity(lmer2b)



(ggplot(pf,aes(season_starting,chickspernest,colour=common_name,shape=common_name,
               linetype=common_name))+
    geom_smooth(method="lm",se=F,fullrange=F)+xlim(1995,2020)+
    geom_point()+theme_bw()+ggtitle("a.")+
    xlab("Breeding season")+ylab("chicks raised per nest")+
    scale_colour_manual(values=c("blue2","green4","red")))/
  
  
  (ggplot(pf,aes(HRK2,chickspernest))+
     geom_hline(yintercept=1,
                linetype="dashed",
                linewidth=1)+
     geom_boxplot()+
     theme_bw()+
     xlab("")+
     ylab("Penguin chicks raised per nest")+
     ggtitle("b.")+
     geom_signif(comparisons = list(c("Biomass > mean, Catch<5%",
                                      "Biomass < mean, Catch<5%"),
                                    c("Biomass < mean, Catch<5%",
                                      "Biomass < mean, Catch>5%"),
                                    c("Biomass > mean, Catch<5%",
                                      "Biomass < mean, Catch>5%")),
                 map_signif_level = F,
                 step_increase = 0.075,
                 test="t.test", 
                 textsize = 3))

### bonus plot

(ggplot()+
  geom_point(data=pf,
             aes(x=CatchS,
                 y=chickspernest,
                 colour=KrillC,
                 shape=KrillC),size=2)+
  theme_bw()+
  theme(panel.spacing.x = unit(1.5, "lines"),
        axis.text.x = element_text(angle=90))+
  geom_smooth(method="lm",se=F,
              data=pf,
              aes(x=CatchS,
                  y=chickspernest,
                  colour=KrillC,linetype=KrillC))+
  scale_colour_manual(values=c("red","blue"),
                      name="Krill availability")+
   scale_shape_manual(values=c("circle","square"),name="Krill availability")+
  scale_linetype_manual(values=c("solid","dashed"),name="Krill availability")+
  #facet_wrap(site_name2~.)+
  xlim(0,50000)+
   
  xlab("Accumulated summer fishing catch (t)")+ 
  ylab("Penguin chicks raised per nest"))





``` 
