---
title: Routine, analysis and suplementary material for the ms "Pygoscelis penguin
  breeding success along the Western Antarctic Peninsula under contrasting krill biomass
  and fixed catch limits"
author: "Lucas Krüger, Maurício Mardones, Francisco Santa Cruz, César Cárdenas"
date: "`r Sys.Date()`"
output: html_document
---

\pagebreak 

# BACKGROUND

This selfcontained document content the codes for: 

- 1. evaluate temporal trends of Pygoscelis penguin breeding success in the South Shetland Islands and Antarctic Peninsula; 

- 2.  evaluate temporal variability of krill biomass in relation to fishing harvest; 

- 3. compare penguin breeding success in periods of low or high krill biomass and low or high fishing catches. 


```{r setup1}
### Set format conditions
rm(list = ls())
dir.fig        <-"fig/"
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = dir.fig,
                      fig.align = 'center',
                      fig.pos = "H",
                      dev = 'jpeg',
                      dpi = 300,
                      fig_width = 8,
                      fig.height = 5,
                      tidy.opts=list(width.cutoff=40),
                      tidy=TRUE)
#XQuartz is a mess, put this in your onload to default to cairo instead
options(bitmapType = "cairo") 
# (https://github.com/tidyverse/ggplot2/issues/2655)
dir.fig        <-"fig/"
```

```{r library}
### Load necessary packages
library(plyr)
library(dplyr) # for summarizing data
library(reshape2)
library(ggplot2)  # plotting 
library(sjPlot)
library(patchwork)
library(lubridate) # to deal with time data
library(udunits2) # to deal with geographical data
library(raster)
library(MCMCglmm) #Bayesian generalized linear mixed models
library(lmerTest)
library(rcompanion)
library(lmPerm)
library(ggsignif)
library(energy)
library(kableExtra)
library(ggthemes)
library(ggpubr)
library(fitdistrplus)
library(AER)
library(easystats)
library(formatR)
```
\pagebreak
# DATA

Four data sources were used: 

- [MAPPPD data](Humphries et al. 2017 https://doi.org/10.1017/S0032247417000055) [@Humphries2017], file named `MAPPPD.Rds` 

- CCAMLR acoustic estimates of krill biomass `CCAMLR_krill_biomass.Rds`, 

- Summarized fishing catch `CCAMLR_krill_fishing_catch.Rds`

- Management strata shapefiles `AMLR_Strata.Rds`. 

Refer to the manuscript for methodological details.

\pagebreak
# ANALISYS ROUTINE

Query for area 48.1


# penguin colonies and temporal analysis for the whole area
```{r, echo=TRUE}

peng<-readRDS("MAPPPD.Rds") 

nests<-subset(peng,
              count_type=="nests",
              select=c(site_name,
                       site_id,
                       longitude_epsg_4326,
                       latitude_epsg_4326,
                       common_name,
                       day,
                       month,
                       season_starting,
                       penguin_count,
                       count_type,
                       vantage,accuracy))  # subset nest counts

chicks<-subset(peng,count_type=="chicks",
               select=c(site_name,
                        site_id,longitude_epsg_4326,
                        latitude_epsg_4326,
                        common_name,
                        day,month,season_starting,penguin_count,
                        count_type,vantage,accuracy)) # subset chick counts

nestsM<-ddply(nests, c("common_name",
                       "site_name",
                       "site_id",
                       "season_starting"), 
              summarise,
              nests=max(penguin_count),
              Lat=mean(latitude_epsg_4326),
              Long=mean(longitude_epsg_4326))

chicksM<-ddply(chicks, c("common_name",
                         "site_name",
                         "site_id",
                         "season_starting"),
               summarise,
               chicks=min(penguin_count),
               Lat=mean(latitude_epsg_4326),
               Long=mean(longitude_epsg_4326))

cpn<-merge(nestsM,chicksM) # cpn stands for Chicks Per Nest


cpn$chickspernest<-cpn$chicks/cpn$nests # breeding success measured as chicks raised per nest


sites<-ddply(cpn, c("site_id"), summarise,
             Ncounts=length(chicks))  # summarise number of counts per site


cpn<-merge(cpn,sites,by="site_id") 


ggplot(cpn,aes(season_starting,chickspernest))+
  geom_point()+
  geom_vline(xintercept = 1990)+
  geom_smooth(method="lm",se=F)+
  facet_wrap(site_id~.)+
  theme_few()+
  theme(axis.text.x = element_text(angle = 90, hjust = 2),
        panel.grid = element_blank())+
  labs(
    x="",
    y="Chicks raised per nest"
  )

#further filters 

cpn<-subset(cpn,season_starting>1989)

shapiro.test(cpn$chickspernest) # not normal

cpn.q <- quantile(cpn$chickspernest, probs=c(.3, .7), na.rm = FALSE)
IQR.p <- IQR(cpn$chickspernest)

Lower <- cpn.q[1] - 1.5*IQR.p
Upper <- cpn.q[2] + 1.5*IQR.p 

cpnS <- subset(cpn, chickspernest > Lower & chickspernest < Upper)

cpn<-subset(cpnS,Ncounts>6) # only colonies with more than 6 counts

ggplot(cpn,aes(season_starting, chickspernest,colour=common_name))+
  geom_smooth(method="lm",se=F)+
  geom_point()+theme_bw()+
  facet_wrap(site_name~.) # Port Charcot & Orne colony still has 3-count data for gentoos

cpn<-subset(cpn,common_name!="gentoo penguin"|site_name!="Port Charcot")
cpn<-subset(cpn,common_name!="gentoo penguin"|site_name!="Orne Islands")


shapiro.test(cpn$chickspernest) # normal if eliminate outliers

bartlett.test(cpn$chickspernest,cpn$common_name)
bartlett.test(cpn$chickspernest,cpn$site_id)


plotdist(cpn$chickspernest,"norm",para=list(mean=mean(cpn$chickspernest), sd=sd(cpn$chickspernest)))



cpn$site_id2<-factor(cpn$site_id,levels=c("LLAN","ARDL","BART","SHIR","HALF","ENTR",
                                          "BROW","SPIP","ORNE","GEOR","LITC","DOBE","DAMO","LOCK",
                                          "JOUG","NEKO","ALMI","PCHA","PLEN","PETE"))  # order by location latitude

cpn$site_name2<-factor(cpn$site_name,
                       levels=c("Llano Point","Ardley Island",
                                "Barton Peninsula",
                                "Cape Shirreff","Half Moon Island",
                                "Entrance Point",
                                "Brown Bluff","Spigot Peak Point",
                                "Orne Islands",
                                "Georges Point (Ronge Island)","Litchfield Island",
                                "Dorian Beacon","Dorian Bay/Damoy Point","Port Lockroy",
                                "Jougla Point","Neko Harbor (Andvord Bay)",
                                "Brown Station","Port Charcot",
                                "Pleneau Island","Petermann Island"))  # order by location latitude

ggplot(cpn,aes(season_starting, chickspernest,
    colour=common_name,shape=common_name,linetype=common_name))+
  scale_colour_manual(values=c("black","blue","red"))+
  geom_smooth(method="lm",se=F)+
  geom_point(size=2,alpha=0.5)+theme_bw()+theme(panel.spacing.x = unit(1.5,"lines"))+
  xlab("Breeding season")+ylab("Breeding success (chicks raised per nest)")+
  facet_wrap(site_name2~.)  # figure 2


#species summaries 

length(unique(cpn$site_id)) # number of sites


length(unique(cpn$site_id[cpn$common_name=="adelie penguin"]))
length((cpn$site_id[cpn$common_name=="adelie penguin"]))

length(unique(cpn$site_id[cpn$common_name=="chinstrap penguin"]))
length((cpn$site_id[cpn$common_name=="chinstrap penguin"]))

length(unique(cpn$site_id[cpn$common_name=="gentoo penguin"]))
length((cpn$site_id[cpn$common_name=="gentoo penguin"]))


cpn$zss<-scale(cpn$season_starting,scale=T,center=T)

lmer1<-lmer(chickspernest~zss+(zss|common_name),data=cpn) # convergence issues, therefore, lets try a simpler method
summary(lmer1)
ranova(lmer1)

#calculate a temporal trend for each site and species
slope<-cpn %>%
  group_by(site_name2,common_name) %>%
  do({
    mod=glm(chickspernest~season_starting,
            data=.)
    data.frame(Intercept=coef(mod)[1],
               Slope=coef(mod)[2])
  })

sites<-ddply(cpn, c("common_name","site_name2","site_id"), summarise,
             
             Lat=mean(Lat),
             Long=mean(Long))
slope

slst<-merge(sites,slope)
ggplot(slst,aes(Lat,Slope))+geom_point()

slst$locat<-ifelse(slst$Lat<(-63.2),"Peninsula","South Shetlands") #location category
summary(as.factor(slst$locat))

shapiro.test(slst$Slope) # barely normal

bartlett.test(slst$Slope,slst$locat) # variances are homogeneous between locations

bartlett.test(slst$Slope,slst$common_name)# variances are marginally homogeneous between species

plotdist(slst$Slope,"norm",para=list(mean=mean(na.omit(slst$Slope)), sd=sd(na.omit(slst$Slope))))

# compare locations


lmlat<-lm(Slope~locat,data=slst)  
summary(lmlat)
anova(lmlat)

# since we checked a priori  distribution and homogeneity, lets only check predictions
posterior_predictive_check(lmlat,iterations=300)

ptt.lat<-pairwise.t.test(slst$Slope,slst$locat,p.adjust.method = "BH",pool.sd = T)


#compare species
lmsp<-lm(Slope~common_name,data=slst)  
summary(lmsp)
anova(lmsp)

# since we checked a priori  distribution and homogeneity, lets only check predictions
posterior_predictive_check(lmsp,lmlat,iterations=300)

ptt.sp<-pairwise.t.test(slst$Slope,slst$common_name,p.adjust.method = "BH",pool.sd = T)
p.sp<-ptt.sp$p.value

ptt.lat$p.value # create a data frame with statistic results:

p.lat<-data.frame(group1="South Shetlands",group2="Peninsula",p.value="p=0.051")

ptt.sp$p.value # create a data frame with statistic results:

p.sp<-rbind(data.frame(group1="adelie penguin",group2="chinstrap penguin",p.value="n.s."),
            data.frame(group1="gentoo penguin",group2="chinstrap penguin",p.value="n.s."),
            data.frame(group1="adelie penguin",group2="gentoo penguin",p.value="n.s."))


(ggplot(slst,aes(locat,Slope))+
    geom_hline(yintercept = 0,linetype="dashed")+
    geom_boxplot(fill="grey")+
    theme_bw()+xlab("")+ylab("Colony-level temporal trend")+
    stat_pvalue_manual(p.lat,label="p.value",y.position = max(slst$Slope)+0.01)+
    ggtitle(label="a. Colony location"))+
  
  
  (ggplot(slst,aes(common_name,Slope))+
     geom_hline(yintercept = 0,linetype="dashed")+
     geom_boxplot(fill="grey")+
     theme_bw()+xlab("")+ylab("")+
     stat_pvalue_manual(p.sp[1,1:3],label="p.value",y.position = max(slst$Slope))+
     stat_pvalue_manual(p.sp[2,1:3],label="p.value",y.position = max(slst$Slope)+0.01)+
     stat_pvalue_manual(p.sp[3,1:3],label="p.value",y.position = max(slst$Slope)+0.02)+
     ggtitle(label="b. Species")) 




rm(list= ls()[! (ls() %in% c('cpn'))])
```



### krill and fishery data 

krill acoustic biomass from "WG-ASAM Results from the WG-ASAM Intersessional e-Group on Krill Biomass Estimates from Acoustic Surveys; 2021;" data from WG-ASAM e-group (2021) and subset the strata where fishing has been consistent

Fishing data from CCAMLR, this is the raw data, not available freely (only the CCAMLR secretariat is allowed to distribute it) 


```{r,echo=TRUE}
### Load krill acoustic dataand subset to the target strata


krill<-readRDS("CCAMLR_krill_biomass.Rds")  
krill2<-subset(krill, Strata=="Bransfield"|Strata=="West") 


### Load and prepare fishery data 

kf0<-read.csv("C1_Sect.csv") # ps: this data is not available here, only the already summarized data resulting from next steps

kf0$CatchT<-kf0$KrillCaughtKG/1000  ### catch in tones
kf0$ts<- as.POSIXct(strptime(kf0$Day,format="%m/%d/%Y" ,tz="GMT")) 
kf0$month<-month(kf0$ts)
kf0$FSeason<-ifelse(kf0$month>11,
                    kf0$CalendarYear,kf0$CalendarYear-1)


kf0$Kseason<-kf0$FSeason+1
kf<-kf0


strata<-readRDS("AMLR_STRATA.Rds")  
crs=CRS( "+proj=longlat +datum=WGS84 +no_defs")
kcoords<-coordinates(data.frame(x=kf$FishingLon,y=kf$FishingLat))
kf.spdf<-SpatialPointsDataFrame(kcoords,kf,proj4string = crs)
kf.strata<-over(kf.spdf,strata)
kf.spdf$Strata<-kf.strata$Strata
kf.spdf<-subset(kf.spdf,FishingLon<(-50))  # eliminate the South Orkney Data 

kf.spdf$Year<-kf.spdf$Kseason

#ggplot(data.frame(kf.spdf),aes(Kseason,CalendarYear,colour=as.factor(month)))+geom_point()

kfMo<-subset(kf.spdf,month=="12"|month=="1"|month=="2"|month=="3") 
fcr2<-ddply((data.frame(kfMo)), c("Year","Strata"), summarise,
            CatchS=sum(CatchT))  ### total catch for each year and strata

summary(fcr2) ### CatchS is catch in Ton
kr<-data.frame(krill[1],krill[2],krill[14]) # keep only needed variables
kmfcr<-merge(kr,fcr2,by=c("Strata","Year"),all=T)  # merge krill and fishery data 
kmfcr2<-subset(kmfcr,Year<2019 & Year>1994)

summary(kmfcr2$amlrbiomass[kmfcr2$Strata=="Bransfield"]) 
summary(kmfcr2$amlrbiomass[kmfcr2$Strata=="West"])
kmfcr2$amlrbiomass[is.na(kmfcr2$amlrbiomass) & kmfcr2$Strata=="Bransfield"]<-392888# 1st qu
kmfcr2$amlrbiomass[is.na(kmfcr2$amlrbiomass) & kmfcr2$Strata=="West"]<-752566# 1st qu

summary(kmfcr2$CatchS[kmfcr2$Strata=="West"])
summary(kmfcr2$CatchS[kmfcr2$Strata=="Bransfield"])
kmfcr2$CatchS[is.na(kmfcr2$CatchS) & kmfcr2$Strata=="West"]<-0 # 1st qu
kmfcr2$CatchS[is.na(kmfcr2$CatchS) &  kmfcr2$Strata=="Bransfield"]<-0 # 1st qu
kmfcr2$Strata<-factor(kmfcr2$Strata,levels=c("West","Bransfield"))
summary(kmfcr2$amlrbiomass/1000)

kmfcr2$CatchK<-kmfcr2$CatchS/kmfcr2$amlrbiomass # harvest rate 
kmfcr2$State[(kmfcr2$amlrbiomass/1000)<1251.728 & kmfcr2$Strata=="West"]<-"Biomass < mean"
kmfcr2$State[(kmfcr2$amlrbiomass/1000)<802.284 & kmfcr2$Strata=="Bransfield"]<-"Biomass < mean"
kmfcr2$State[(kmfcr2$amlrbiomass/1000)<200]<-"Near or below catch limit"
kmfcr2$State[is.na(kmfcr2$State)]<-"Biomass > mean"

kmfcr2$State<-factor(kmfcr2$State,levels=c("Biomass > mean","Biomass < mean","Near or below catch limit"))



fig3a<-ggplot()+
  geom_hline(yintercept=155,linetype="dotted",colour="red")+
  geom_hline(yintercept=1251.728,linetype="dashed")+
  geom_hline(yintercept=802.284,linetype="dashed")+
  geom_smooth(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
              aes(x=Year,y=(amlrbiomass/1000)),
              method="lm",se=F,
              fullrange=F,
              formula=y~x)+
  xlim(1995,2018)+
  geom_point(data=subset(kmfcr2,
                         Strata=="Bransfield"|Strata=="West"),
             aes(x=Year,y=(amlrbiomass/1000),
                 colour=State),size=2)+
  theme_bw()+
  facet_wrap(~Strata)+
  ggtitle(label="a. krill biomass")+
  scale_colour_manual(values=c("green2","yellow3","red2"))+
  ylab("thousand tonnes")+xlab("") # figure X


fig3b<-ggplot()+
  geom_hline(yintercept=5,linetype="dotted",colour="red")+geom_point()+
  
  geom_smooth(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
              aes(x=Year,y=(CatchK*100)),method="lm",se=F,fullrange=F,span=0.9)+xlim(1995,2018)+
  geom_point(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
             aes(x=Year,y=(CatchK*100),colour=State),size=2)+theme_bw()+facet_wrap(~Strata)+
  ggtitle(label="b. krill caught biomass")+
  scale_colour_manual(values=c("green2","yellow3","red2"))+
  ylab("% of catched biomass") # figure X


fig3c<-ggplot()+
  geom_hline(yintercept=5,linetype="dashed")+geom_point()+
  geom_vline(xintercept=1251.728,linetype="dashed")+
  geom_vline(xintercept=802.284,linetype="dashed")+
  geom_smooth(data=subset(kmfcr2,Strata=="Bransfield"|Strata=="West"),
              aes(x=(amlrbiomass/1000),
                  y=(CatchK*100)),
              method="gam",se=F,
              fullrange=F,span=0.9)+
  geom_point(data=subset(kmfcr2,
                         Strata=="Bransfield"|Strata=="West"),
             aes(x=(amlrbiomass/1000),
                 y=(CatchK*100),
                 colour=State),size=2)+
  theme_bw()+facet_wrap(~Strata)+
  ggtitle(label="c. availability vs catch")+
  scale_colour_manual(values=c("green2","yellow3","red2"))+
  ylab("% of catched biomass")+ 
  xlab("Krill biomass (million tonnes)") # figure X

fig3a/fig3b/fig3c # fig 3

kmfcr3<-na.omit(kmfcr2)

```

#is krill biomass reducing? Test if biomass in periods of high krill productivity is decreasing

```{r}
### removing outliers 
quartiles <- quantile(log(kmfcr3$amlrbiomass), probs=c(.2, .8), na.rm = FALSE)
IQR <- IQR(log(kmfcr3$amlrbiomass))

Lower <- quartiles[1] - 1.5*IQR
Upper <- quartiles[2] + 1.5*IQR 

data_no_outlier <- subset(kmfcr3, log(amlrbiomass) > Lower & log(amlrbiomass) < Upper)

data_no_outlier$State[data_no_outlier$State=="Near or below catch limit"]<-"Biomass < mean"

shapiro.test(log(data_no_outlier$amlrbiomass)[data_no_outlier$State=="Biomass > mean"]) # normal
bartlett.test(log(data_no_outlier$amlrbiomass)[data_no_outlier$State=="Biomass > mean"],data_no_outlier$Strata[data_no_outlier$State=="Biomass > mean"]) # homogeneous variance


plotdist(log(data_no_outlier$amlrbiomass[data_no_outlier$State=="Biomass > mean"]),"norm",
         para=list(mean=mean(log(data_no_outlier$amlrbiomass[data_no_outlier$State=="Biomass > mean"])), 
                   sd=sd(log(data_no_outlier$amlrbiomass[data_no_outlier$State=="Biomass > mean"]))))

glm1<-lm(log(amlrbiomass)~Year+Strata,
         data=subset(data_no_outlier,State=="Biomass > mean"))


posterior_predictive_check(glm1,iterations=300)
plot(check_outliers(glm1))
plot(check_collinearity(glm1))


summary(glm1)

anova(glm1) # krill biomass reduced significantly in time

plot_model(glm1,type="pred")


rm(list= ls()[! (ls() %in% c('cpn','kmfcr2',"strata","crs"))])

```
### Penguins and fishery

### merge all previous datasets to answer the questions: does increased catches can affect penguin breeding success in a decreasing krill biomass context?

```{r}

pcoords<-coordinates(data.frame(cpn[6:5])) 
plot(pcoords)

p.spdf<-SpatialPointsDataFrame(pcoords,cpn,proj4string = crs)

identicalCRS(p.spdf,strata)
p.strata<-over(p.spdf,strata)
p.spdf$Strata<-p.strata$Strata
p.spdf$StrataP<-p.spdf$Strata

p.df<-data.frame(p.spdf)
peng<-data.frame(p.df) 
summary(as.factor(peng$StrataP))

peng$Year<-peng$season_starting

peng.f<-merge(peng,kmfcr2,by=c("Strata","Year"))  ## merge 

summary(as.factor(peng.f$site_id2))

pengf<-na.omit(subset(peng.f,StrataP==Strata))#if penguin and fishing strata coincides, then it is right

summary(as.factor(pengf$site_id))

pengf$harvest<-pengf$CatchS/pengf$amlrbiomass # catch per unit of krill biomass (harvest rate)

rm(list= ls()[! (ls() %in% c("pengf"))])

ggplot(pengf,aes(harvest,chickspernest))+ #figure S6
  geom_point()+
  theme_bw()+
  xlab("% of caught biomass (harvest rate)")+
  ylab("chicks raised per nest")+
  geom_vline(xintercept=0.05,linetype="dashed") #5% catch

pengf$HR<-ifelse(pengf$harvest>0.05,">5%","<5%")
pengf<-na.omit(pengf)
pengf$KrillC<-pengf$State
summary(as.factor(pengf$KrillC))

pengf$KrillC[pengf$KrillC=="Near or below catch limit"]<-"Biomass < mean"

ddply(pengf, c("HR","KrillC"), summarise,
      ncounts=length(chickspernest))

shapiro.test(pengf$chickspernest)# normal

plotdist((pengf$chickspernest),"norm",para=list(mean=mean((pengf$chickspernest)), 
                                                 sd=sd((pengf$chickspernest))))

summary(as.factor(pengf$HR))

summary(as.factor(pengf$KrillC))

unique(pengf$site_id)
summary(as.factor(pengf$site_id))

pengf$HRK<-paste(pengf$KrillC,pengf$HR,sep=", Catch") # harvest rate and krill categories
summary(as.factor(pengf$HRK)) 
pengf$HRK2<-factor(pengf$HRK,levels=c("Biomass > mean, Catch<5%",
                                        "Biomass < mean, Catch<5%",
                                        "Biomass < mean, Catch>5%"))

bartlett.test(pengf$chickspernest,pengf$HRK2) # homogeneity of variances

summary(as.factor(pengf$HRK2))

lmer2<-lmer(chickspernest~HRK2+(1|site_id),
            data=pengf)
anova(lmer2,
      ddf="Satterthwaite",
      type = "III")


summary(lmer2)

ranova(lmer2)

plot_model(lmer2,type="re") # Cape Shirreff is marginally different
pf<-subset(pengf,site_id!="SHIR") # use the other two sites for the next analysis


pf$lcs<-log(pf$CatchS+1)
pf$LKrill<-log(pf$amlrbiomass)

shapiro.test(pf$chickspernest) # normal


lm3<-lm(chickspernest~lcs*LKrill,
            data=pf)
lm3b<-lm(chickspernest~lcs+LKrill,
          data=pf)   # to check for collinearity between variables


summary(lm3)
anova(lm3)
plot_model(lm3,type="emm",terms=c("lcs[all]","LKrill[13,14]"))

posterior_predictive_check(lm3,iterations=300)
check_outliers(lm3)
check_collinearity(lm3) # the program suggest check without interaction terms, therefore:
check_collinearity(lm3b) # it is ok
check_homogeneity(lm3)
check_heteroscedasticity(lm3)

(ggplot(pengf,aes(HRK2,chickspernest))+
  geom_hline(yintercept=1,
             linetype="dashed",
             linewidth=1)+
  geom_boxplot()+
  theme_bw()+
  xlab("")+
  ylab("Penguin chicks raised per nest")+
    ggtitle("a.")+
  geom_signif(comparisons = list(c("Biomass > mean, Catch<5%",
                                   "Biomass < mean, Catch<5%"),
                                 c("Biomass < mean, Catch<5%",
                                   "Biomass < mean, Catch>5%"),
                                 c("Biomass > mean, Catch<5%",
                                   "Biomass < mean, Catch>5%")),
              map_signif_level = F,
              step_increase = 0.075,
              test="t.test", 
              textsize = 3))/



(ggplot()+
  geom_point(data=pf,
             aes(x=CatchS,
                 y=chickspernest,
                 colour=KrillC,
                 shape=KrillC),size=2)+
  theme_bw()+
  theme(panel.spacing.x = unit(1.5, "lines"),
        axis.text.x = element_text(angle=90))+
  geom_smooth(method="lm",se=F,
              data=pf,
              aes(x=CatchS,
                  y=chickspernest,
                  colour=KrillC,linetype=KrillC))+
  scale_colour_manual(values=c("red","blue"),
                      name="Krill availability")+
   scale_shape_manual(values=c("circle","square"),name="Krill availability")+
  scale_linetype_manual(values=c("solid","dashed"),name="Krill availability")+
  #facet_wrap(site_name2~.)+
  xlim(0,50000)+
   ggtitle("b.")+
  xlab("Accumulated summer fishing catch (t)")+ 
  ylab("Penguin chicks raised per nest"))


```